Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-07 sections/01-introduction.tex
Update on Overleaf.

One important aspect of testing the consistency of the new method with the gold standard is to adequately validate if the new method is measuring changes in the target variable in the right direction, when the gold standard detects changes during the measurement process. 
Ideally, the signs of the changes between two consecutive points in time (with a defined time interval) measured by the new method and the gold standard method should always be the same. 
In this case, we call the new method trending perfect in line with the gold Stadnard method and refer to this type of agreement as trendability. 
This type of consideration of the trend ability of a measurement method to the gold standard has also recently gained importance in the literature \cite{saugel2015tracking, hiraishi2021concordance}. 
In (\cite{hiraishi2021concordance}), the authors proposed a new concordance rate for the four-quadrant diagram, which is based on the multivariate normal distribution and takes into account the correlation between the data of the individual subjects.

>>>>

One important aspect of testing the consistency of the new method with the gold standard is to adequately validate if the new method is measuring changes in the target variable in the right direction, when the gold standard detects changes during the measurement process. 
Ideally, the signs of the changes between two consecutive points in time (with a defined time interval) measured by the new method and the gold standard method should always be the same. 
In this case, we call the new method trending perfect in line with the gold Stadnard method and refer to this type of agreement as trendability. 
This type of consideration of the trend ability of a measurement method to the gold standard has also recently gained importance in the literature \cite{saugel2015tracking, saugel2018error, hiraishi2021concordance}.

%In (\cite{hiraishi2021concordance}), the authors proposed a new concordance rate for the four-quadrant diagram, which is based on the multivariate normal distribution and takes into account the correlation between the data of the individual subjects.
